### 2010-06-11 subarchitectures/visualization.sa/trunk/doc/v11n.tex
v11n: docs

>>>>

\subsection{HTML documents}

The display server renders HTML documents with Qt-WebKit. It provides the
sturcture of the HTML document while display clients provide chunks of
HTML code that goes into the head or the body of the document.
The client-side interface for defining HTML document chunks is:

\begin{Verbatim}[fontsize=\scriptsize,gobble=3]
   void setHtml(const std::string& id, const std::string& partId,
         const std::string& htmlData); 
   void setHtmlHead(const std::string& id, const std::string& partId,
         const std::string& htmlData); 
\end{Verbatim}

Chunks for the head and the body part of a document are independent. This means
that a chunk in the head may have the same partId as a chunk in the body of
a document. When a part is removed from a document, the chunks for the head
and the body with the requested partId are removed.
\todo{TODO: ICE interface for removing (parts of) objects is still missing}
